Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-04 bbbq_article.tex
Is it significant the overlapping of one residue for MHC binding? No. Fix https://github.com/richelbilderbeek/bbbq_article/issues/242

To prove this point, we did exactly the same analysis 
as shown in Figure \ref{fig:bbbq_1_smart_results},
yet with defining a TMH-derived epitope as an epitope that overlaps with a TMH
for at least 2 AAs, as shown in Figure \ref{fig:bbbq_1_smart_results_2aas}.
As these two figures look identical \richel{TODO: they are indentical,
need to redo the calculation then}, 
we also added the counts as numbers,
with Table \ref{tab:tmh_binders_mhc2_2aas} showing the same data
as \ref{tab:tmh_binders_mhc2}, except the former uses 2 AAs overlap.
Likewise, Table \ref{tab:tmh_binders_mhc1_2aas} showing the same data
as \ref{tab:tmh_binders_mhc1}, except the former uses 2 AAs overlap.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_2aa_results/fig_f_tmh_2_panel.png}
  \caption{
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The pair of dashed lines in each plot indicate the lower and upper bound of the 99\% confidence interval.
    See supplementary Tables \ref{tab:tmh_binders_mhc2_2aas} and \ref{tab:tmh_binders_mhc1_2aas}
    for the exact TMH and  epitope counts.
  }
  \label{fig:bbbq_1_smart_results_2aas}
\end{figure}

>>>>

To prove this point, we did exactly the same analysis 
as shown in Figure \ref{fig:bbbq_1_smart_results},
yet with defining a TMH-derived epitope as an epitope that overlaps with a TMH
for at least 2 AAs, as shown in Figure \ref{fig:bbbq_1_smart_results_2aas}.
As these two figures look identical, 
we also added the counts as numbers,
with Table \ref{tab:tmh_binders_mhc2_2aas} showing the same data
as \ref{tab:tmh_binders_mhc2}, except the former uses 2 AAs overlap.
Likewise, Table \ref{tab:tmh_binders_mhc1_2aas} showing the same data
as \ref{tab:tmh_binders_mhc1}, except the former uses 2 AAs overlap.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_2aa_results/fig_f_tmh_2_panel.png}
  \caption{
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs (for at least two amino acids) 
    for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The pair of dashed lines in each plot indicate the lower and upper bound of the 99\% confidence interval.
    See supplementary Tables \ref{tab:tmh_binders_mhc2_2aas} and \ref{tab:tmh_binders_mhc1_2aas}
    for the exact TMH and  epitope counts.
  }
  \label{fig:bbbq_1_smart_results_2aas}
\end{figure}
